Model Search in Relational Domains

### 2016-10-21 decision.tex

ACDCL supports several decision heuristics namely, {\em ordered}, 
{\em longest-range}, {\em random}, {\em relational} and 
{\em Berkmin}~\cite{eugoldberg07} decision heuristics.  
The {\em ordered} decision heuristics creates an ordering among non-singleton 
meet irreducibles, thereby making decisions on meet irreducibles that involve 
conditional variables (variables that appear in conditional branches) first 
before choosing meet irreducibles with numerical variables.  
The ordering heuristic is similar to trace partitioning~\cite{toplas07}.

The {\em longest-range} heuristics simply keeps track of the
interval $[l,u]$ range ($r=u-l$) of a meet irreducible and chooses 
a meet irreducible with the longest range value.  This ensures a 
fairness policy in selecting a variable since it guarantees that 
the intervals of meet irreducibles are uniformly restricted.  
%
The {\em random} decision heuristics arbitrarily picks a meet irreducible  
for making decision. 
%
The {\em relational} decision heuristics is only relevant for relational 
abstract domains.  
%
Whereas, a {\em berkmin} decision heuristics is inspired 
from decision heuristic used in Berkmin~\cite{eugoldberg07} SAT solver.  
The berkmin heuristic is currently implemented for interval constraints only.  
The heuristic keeps track of the activity of an interval meet irreducible 
that participate in conflict clauses. 
\Omit {
as well as variables that actively contribute to conflicts but do not explicitly 
appear in conflict clauses.  The set of conflict clauses is 
organized chronologically with the top clause 
as the one deduced in the last.  A branching variable is chosen among the 
free variables whose literals are in the top unsatisfied conflict clause.  
A similar decision heuristics is also implemented in Chaff~\cite{chaff} SAT 
solver, that computes the activity of a variable as the number of occurrences 
of that variable in conflict clauses only. 
}
%
A bound of a meet irreducible is heuristically chosen to be an approximation of the 
arithmetic average of the current bounds.  However, the polarity ($\leq$ or $\geq$) 
of a meet irreducible is chosen randomly.

>>>>

ACDCL supports several decision heuristics namely, {\em ordered}, 
{\em longest-range}, {\em random} and 
{\em Berkmin}~\cite{eugoldberg07} decision heuristics.  
The {\em ordered} decision heuristics creates an ordering among non-singleton 
meet irreducibles, thereby making decisions on meet irreducibles that involve 
conditional variables (variables that appear in conditional branches) first 
before choosing meet irreducibles with numerical variables.  
The ordering heuristic is similar to trace partitioning~\cite{toplas07}.

The {\em longest-range} heuristics simply keeps track of the
interval $[l,u]$ range ($r=u-l$) of a meet irreducible and chooses 
a meet irreducible with the longest range value.  This ensures a 
fairness policy in selecting a variable since it guarantees that 
the intervals of meet irreducibles are uniformly restricted.  
%
The {\em random} decision heuristics arbitrarily picks a meet irreducible  
for making decision. 
%
%The {\em relational} decision heuristics is only relevant for relational 
%abstract domains.  
%
Whereas, a {\em berkmin} decision heuristics is inspired 
from decision heuristic used in Berkmin~\cite{eugoldberg07} SAT solver.  
The berkmin heuristic is currently implemented for interval constraints only.  
The heuristic keeps track of the activity of an interval meet irreducible 
that participate in conflict clauses. 
\Omit {
as well as variables that actively contribute to conflicts but do not explicitly 
appear in conflict clauses.  The set of conflict clauses is 
organized chronologically with the top clause 
as the one deduced in the last.  A branching variable is chosen among the 
free variables whose literals are in the top unsatisfied conflict clause.  
A similar decision heuristics is also implemented in Chaff~\cite{chaff} SAT 
solver, that computes the activity of a variable as the number of occurrences 
of that variable in conflict clauses only. 
}
%
A bound of a meet irreducible is heuristically chosen to be an approximation of the 
arithmetic average of the current bounds.  However, the polarity ($\leq$ or $\geq$) 
of a meet irreducible is chosen randomly.

### 2016-10-21 experiments.tex

\paragraph {\textbf{Decision Heuristics}} Figure~\ref{prop-dec}(b) presents a 
visualization of different decision heuristics in ACDCL.  Random heuristic
performs the best for most safe benchmarks and all bit-vector category 
benchmarks.  Whereas, the ordered heuristic performs better for programs 
with conditional branches since it prioritises decisions on meet 
irreducibles that appear in conditional branches over meet irreducibles 
that involve numerical variables.  Whereas, the runtimes for berkmin 
heuristic is slightly greater than the random and ordered heuristic 
for our benchmarks.

>>>>

\paragraph {\textbf{Decision Heuristics}} Figure~\ref{prop-dec}(b) presents a 
visualization of the performance of different decision heuristics in ACDCL.  
Note that the runtimes for all decision heuristics are obtained with multi-way 
propagtion strategy.  The runtimes are very close, but we observe some key
characteristics of these heuristics.  Berkmin heuristic performs consistently 
well for most safe benchmarks and all bit-vector category benchmarks.  Whereas, 
the ordered heuristic performs better for programs with conditional branches 
since it prioritises decisions on meet irreducibles that appear in conditional 
branches over meet irreducibles that involve numerical variables.  Whereas, 
the runtimes for random heuristic is marginally higher than the other two.  This 
suggest that domain-specific decision heuristics are important for ACDCL.
